SoK: Web Application Attack Defenses (in Question)

### 2014-10-08 docs/questioning.tex
minor fixes
minor typo

The basic problem behind web application attacks involves
the absence of input validation. By taking advantage of
this, attackers can inject either code into
applications to perform malicious tasks. Such
an exploit can have different forms depending on the
execution context of the application and the location
of the programming flaw that leads to the attack.

@@

	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 20,8,5 & (241,{\sc nq},0,0)\_a & 39\% & {\sc sql} and {\sc xp}ath injection \\

>>>>

The basic problem behind web application attacks involves
the absence of input validation. By taking advantage of
this, attackers can inject their code into
applications to perform malicious tasks. Such
an exploit can have different forms depending on the
execution context of the application and the location
of the programming flaw that leads to the attack.

@@

	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% & {\sc sql} and {\sc xp}ath injection \\
